CRUSE to Safe Cycling in Ireland

### 2023-10-06 paper.qmd
Fix typo in scenario name heading
Add SIM x-reference

::: {#fig-scenarios}

![](images/paste-7.png)

Distance-mode share graph for Limerick used to communicate the different scenarios. Source: county level view for Limerick in the open access CRUSE Tool at <https://cruse.bike/limerick>.

:::

@@

The Climate Action Plan scenario is loosely based on the Irish Government's [Climate Action Plan 2021](https://www.gov.ie/en/publication/6223e-climate-action-plan-2021/), which contains policies for action to achieve a 51% reduction in overall greenhouse gas emissions by 2030, on a path towards net-zero by 2050.
For transport, this includes 500,000 extra walking, cycling and public transport trips per day by 2030.
In terms of car travel, the target is to "Increas[e] the proportion of kilometres driven by passenger electric cars to between 40 and 45% by 2030, in addition to a reduction of 10% in kilometres driven by the remaining internal combustion engine cars."
This equates to a 5.5 to 6% reduction in total car km driven.

@@

## Ebike

@@

>>>>

::: {#fig-scenarios}
![](images/paste-7.png)

Distance-mode share graph for Limerick used to communicate the different scenarios.
Source: county level view for Limerick in the open access CRUSE Tool at <https://cruse.bike/limerick>.
:::

@@

The Climate Action Plan scenario is loosely based on the Irish Government's [Climate Action Plan 2021](https://www.gov.ie/en/publication/6223e-climate-action-plan-2021/), which contains policies for action to achieve a 51% reduction in overall greenhouse gas emissions by 2030, on a path towards net-zero by 2050.
For transport, this includes 500,000 extra walking, cycling and public transport trips per day by 2030.
In terms of car travel, the target is to "Increas\[e\] the proportion of kilometres driven by passenger electric cars to between 40 and 45% by 2030, in addition to a reduction of 10% in kilometres driven by the remaining internal combustion engine cars." This equates to a 5.5 to 6% reduction in total car km driven.

@@

### Ebike

@@

The CRUSE Tool is an open access web application for strategic cycle network planning and prioritisation of road safety interventions across Ireland.
Building on previous work, it provides a nationally consistent evidence base, providing valuable insights to planners and other stakeholders in the transport planning process, at national and local levels.
Because the results are available at the route segment level, the tool can be used to identify 'weak links' in the cycle network, and to prioritise investment in cycling infrastructure.
Furthermore, the provision of the evidence in a free and publicly available website, hosted at [cruse.bike](https://cruse.bike), means that it can be used by anyone, encouraging wider participation and more evidence-based debate about transport planning.

A key feature of the project methodologically is its calculation of current and future potential not only for travel to work and travel to school, but also for other trip purposes, including recreational trips.
This required the development of spatial interaction models and estimation of the relative attractiveness of different destinations for different trip purposes, an area of active research where new developments could be incorporated into the tool in future [@hasova2022].
